\chapter{Discussion}

\section{Timeline}
The project timeline is structured to complete development by mid-February, allowing time for a personal
test run before starting external user testing. User tests are planned for March - April, followed by evaluation
and thesis writing in April - May.

\begin{itemize}
  \item \textbf{Now - mid February:} Finalize prototype to a ``test-ready'' state.
  \begin{itemize}
    \item Complete remaining core features.
    \item Content completion for the planned missions/parts and balancing of step goals.
    \item Internal QA: bug fixing, usability improvements, and edge-case handling (permissions, background step tracking).
  \end{itemize}

  \item \textbf{Mid February - end February:} Personal test run.
  \begin{itemize}
    \item Run the prototype daily under realistic conditions to validate the gameplay loop.
    \item Verify data collection works reliably over multiple days.
    \item Identify and fix critical issues before involving participants.
  \end{itemize}

  \item \textbf{March - April:} User testing phase.
  \begin{itemize}
    \item Distribute APK to participants and support installation.
    \item Collect quantitative logs and qualitative feedback (survey/interview).
  \end{itemize}

  \item \textbf{April:} Evaluation phase.
  \begin{itemize}
    \item Analyze engagement patterns over time and summarize qualitative feedback.
    \item Answer research questions using collected data.
    \item Derive implications for design improvements and discuss limitations.
  \end{itemize}

  \item \textbf{April - May:} Thesis writing and finalization.
  \begin{itemize}
    \item Integrate evaluation findings with theory (Octalysis/BCW) and prior work.
    \item Final proofreading, formatting, and submission preparation.
  \end{itemize}
\end{itemize}